% !TeX root = ../thesis.tex

% 中英文摘要和关键字
\begin{cnabstract} 
  以江苏斯尔邦石化有限公司 LDPE/EVA 联合装置循环冷却水系统的压力缓冲需求为背景，完成冷媒膨胀罐（位号 22-V-1810）的机械设计。设备采用立式圆筒形焊接结构，筒体内径 $1800$ mm、切线长度 $1700$ mm、有效容积 $5.5$ m³；主体材料 Q345R 正火钢板，上、下标准椭圆形封头，圆筒形焊制裙座支承。设计遵循 GB/T 150—2024 及 TSG 21—2016，设计压力 $0.80$ MPa(g)（含全真空），设计温度 $170$ ℃。经计算，筒体与封头名义厚度确定为 $14$ mm；操作工况环向应力 $67.7$ MPa，安全裕度 $2.33$；全真空许用外压力 $0.125$ MPa，水压试验应力 $86.3$ MPa。各项强度指标满足规范要求，设计结果可用于工程制造。
 \\
 \\
 \heiti 关键词：\songti 冷媒膨胀罐；压力容器；Q345R 钢；强度计算；外压稳定性；开孔补强；水压试验
\end{cnabstract} 
  
%%======English Abstract=======%%
\begin{enabstract}
  A refrigerant expansion vessel (Tag No.~22-V-1810) is designed for the recirculating cooling water system of a LDPE/EVA unit in Jiangsu Sierbang Petrochemical's methanol-to-olefins project. The vertical cylindrical welded vessel has an inner diameter of $1800$~mm, a tangent-to-tangent length of $1700$~mm, and an effective volume of $5.5$~m\textsuperscript{3}. Constructed of Q345R steel with standard elliptical heads and a cylindrical welded skirt, the vessel complies with GB/T~150—2024 and TSG~21—2016. The nominal shell and head thickness is $14$~mm, satisfying internal pressure ($0.80$~MPa(g)) and full-vacuum ($-0.1013$~MPa(g)) stability criteria. The operating hoop stress is $67.7$~MPa (safety factor $2.33$). The allowable external pressure of $0.125$~MPa exceeds the vacuum load. Hydrostatic test stress is $86.3$~MPa, well below the $263.9$~MPa limit. All GB/T~150—2024 criteria are satisfied, and the complete manufacturing and inspection program qualifies the design for engineering fabrication.
  \\
  \\
  \textbf{Keywords:} Refrigerant expansion vessel; pressure vessel; Q345R; strength calculation; external pressure stability; skirt support; opening reinforcement; GB/T~150
\end{enabstract}
